Machine Learning for Handwriting Recognition: Algorithms and Techniques

### 2023-11-09 Manuscript/Manuscript.tex
Added Paragraph 3

\paragraph{Data Collection}
In tackling handwriting recognition tasks, selecting the right libraries and packages is paramount for achieving robust training results. Noteworthy libraries include TensorFlow and Keras which offer a plethora of deep learning functionalities crucial for building and training neural networks adept at recognizing handwritten characters. Additionally, PyTorch is a highly flexible and dynamic open-source machine learning framework that is particularly known for its ease of use and suitability for a variety of tasks, including handwriting recognition. It allows for the construction, training, and evaluation of deep neural networks with a straightforward and Pythonic interface.On the other hand, the MNIST dataset is a classic in the machine learning community, comprising 60,000 training images and 10,000 testing images of handwritten digits from 0 to 9. Each image is grayscale and 28x28 pixels in size. This dataset has been widely used as a benchmark to evaluate and compare different algorithms' performance in the domain of handwriting recognition. When utilized in conjunction with PyTorch, the MNIST dataset can serve as a powerful tool to develop and evaluate handwriting recognition models efficiently. 
\paragraph{Paragraph 3}

>>>>

\paragraph{Data Collection}
In tackling handwriting recognition tasks, selecting the right libraries and packages is paramount for achieving robust training results. Noteworthy libraries include TensorFlow and Keras which offer a plethora of deep learning functionalities crucial for building and training neural networks adept at recognizing handwritten characters. Additionally, PyTorch is a highly flexible and dynamic open-source machine learning framework that is particularly known for its ease of use and suitability for a variety of tasks, including handwriting recognition. It allows for the construction, training, and evaluation of deep neural networks with a straightforward and Pythonic interface.On the other hand, the MNIST dataset is a classic in the machine learning community, comprising 60,000 training images and 10,000 testing images of handwritten digits from 0 to 9. Each image is grayscale and 28x28 pixels in size. This dataset has been widely used as a benchmark to evaluate and compare different algorithms' performance in the domain of handwriting recognition. When utilized in conjunction with PyTorch, the MNIST dataset can serve as a powerful tool to develop and evaluate handwriting recognition models efficiently.

\paragraph{Fundemental Concepts}
How does the training step work specifically? If we look at the picture, it is composed by 25x25 pixels, just like we mentioned above, and if we cut them into little pieces and then we reorganize them into a one-dimensional column, you will see something like a binary data in this column, it can be shows with 0 if the block is black, and 1 when this block is white. And now, we will be trying to construct the first layer of neural network node, how should we do that, first, we number them up from X0:0 to X0:24, then the first layer of the neural network nodes X1:0 will calculate like this:

\begin{figure}
    \centering
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}
    \includegraphics[width=0.5\textwidth]{Image1.png}
    \vspace{0.5cm}
    \label{fig:my_image_label}
\end{figure}
